Mutual Coherence Minimization \\via Projection Matrices\\ for CSM EENG 515

### 2018-12-10 paper.tex
Update paper.tex

\section{Introduction}
\IEEEPARstart{T}{he} reduction of Mutual Coherence of sensing systems has long plagued
those who need to measure quantities. It is important that if multiple measurements
are taken, that there is not too much redundant information about the underlying 
process being measured. Through Compressive Sensing (CS) techniques, it is possible to achieve
a smaller amount of required measurements. Typically, these techniques involve a sparse
sampling of an over-complete dictionary which could describe the signal being sampled. This 
motivates the question: What is the "best" sparse sampling? \\
Another paragraph here

@@

paper, several norms are used. First we define the $l^\infty$ norm:

@@

This can be thought of as vectorizing $A$, then computing it's vector $l^2$ norm.  To define the vector 
$l^2$ norm:

@@

Eqn~\ref{eq:vecl2} is a commonly used norm and is a member of the $l^p$ norms. Another such member from

@@

Finally, there is one more norm which is used throughout this paper which is the $l^0$ norm. This 

@@

Because this problem uses the $l^0$ norm, the problem is not immediately tractable. Some transformations

@@

One method for transforming this problem, involves transitioning from the $l^0$ norm to the $l^1$ norm.

@@

Another important technique used is the projection onto the $l^1$ ball $\ldots$\\

@@

>>>>

\section{Introduction}
\IEEEPARstart{T}{he} reduction of Mutual Coherence of sensing systems has long plagued
those who need to measure quantities. It is important that if multiple measurements
are taken, that there is not too much redundant information about the underlying 
process being measured. Through Compressive Sensing (CS) techniques, it is possible to achieve
a smaller amount of required measurements. Typically, these techniques involve a sparse
sampling of an over-complete dictionary which could describe the signal being sampled. This 
motivates the question: What is the "best" sparse sampling? \\
This paper examines one method in particular for determining optimal sparse signal 
dictionaries and sampling matrices. First mutual coherence minimization is explored

@@

paper, several norms are used. First we define the $l_\infty$ norm:

@@

This can be thought of as vectorizing $A$, then computing it's vector $l_2$ norm.  To define the vector 
$l_2$ norm:

@@

Eqn~\ref{eq:vecl2} is a commonly used norm and is a member of the $l_p$ norms. Another such member from

@@

Finally, there is one more norm which is used throughout this paper which is the $l_0$ norm. This 

@@

Because this problem uses the $l_0$ norm, the problem is not immediately tractable. Some transformations

@@

One method for transforming this problem, involves transitioning from the $l_0$ norm to the $l_1$ norm.

@@

Another important technique used is the projection onto the $l_1$ ball $\ldots$\\

@@

Lin's method for mutual coherence minimization involves estimating the gradient of the dictionary
($\Delta D$) through a projection onto the $l_1$ ball. $\ldots$ \\
After this factor $V$ has been found:
    \Delta D = M(V + V^T)
And to iterate for new values of D:
    D_{k+1} = \frac{2}{3}
